### 2014-12-12 Documentacion/introduccion.tex
ajustar tamaño de imagenes

        \subfloat[Recontrucción 3D]{\includegraphics[scale=0.17]{img/Reconstruccion/reconstruccion1.png}\label{peladoewconstruidointro}}
    	\subfloat[Seguimiento]{\includegraphics[scale=0.3]{img/Tracking/track1.png}\label{peladoetrackingintro}}  
  \caption{Salidas de los bloques principales del sistema.}
      \label{ejemplotutiintro}
\end{figure}

>>>>

        \subfloat[Recontrucción 3D]{\includegraphics[scale=0.15]{img/Reconstruccion/reconstruccion1.png}\label{peladoewconstruidointro}}
    	\subfloat[Seguimiento]{\includegraphics[scale=0.24]{img/Tracking/track1.png}\label{peladoetrackingintro}}  
  \caption{Salidas de los bloques principales del sistema.}
      \label{ejemplotutiintro}
\end{figure}
